Forecasting interrupted time series

### 2024-01-06 fits.qmd
Added pedestrian plot

We apply the four solutions discussed in @sec-methods. We fit ETS, ARIMA and dynamic ARIMA models to the data, with no transformations used. We have evaluated the methods by using time series cross-validation, with the initial training set comprising the whole of 2019, and subsequent training sets growing by 1 week at a time, to the end of 2021. The test sets are always 3 weeks long. Thus, we have evaluated the forecasts during 2020 and 2021, covering all lockdown periods, and the start of the recovery period. The results are shown in @fig-walkers-plot1.

>>>>

We apply the four solutions discussed in @sec-methods. We fit ARIMA and dynamic ARIMA models to the data, with no transformations used. We have evaluated the methods by using time series cross-validation, with the initial training set comprising the whole of 2019, and subsequent training sets growing by 1 week at a time, to the end of 2021. The test sets are always 3 weeks long. Thus, we have evaluated the forecasts during 2020 and 2021, covering all lockdown periods, and the start of the recovery period. The results are shown in Figures [-@fig-walkers-plot1]--[-@fit-walkers-plot4]

```{r}
#| label: fig-walkers-plot1
#| fig-height: 3
#| fig-cap: "Solution 1: the forecasts do not take into account the lockdown periods, but the ARIMA model is able to adjust to the changing level of the series."
tar_read(walkers_plot1)
```

```{r}
#| label: fig-walkers-plot2
#| fig-height: 3
#| fig-cap: "Solution 2: the forecasts are based on an ARIMA model with a dummy variable indicating when the lockdown periods occurred."
tar_read(walkers_plot2)
```

```{r}
#| label: fig-walkers-plot3
#| fig-height: 3
#| fig-cap: "Solution 3: the lockdown periods are set to missing, and the ARIMA model uses the remaining data to produce forecasts"
tar_read(walkers_plot3)
```

```{r}
#| label: fig-walkers-plot4
#| fig-height: 3
#| fig-cap: "Solution 4: the lockdown periods are replaced with estimated counts based on an ARIMA model applied to the remaining data. Then a new ARIMA model is fitted to the whole data set, and used to produce forecasts."
tar_read(walkers_plot4)
```
